\documentclass[12pt]{article}
\pagestyle{empty}
\usepackage[a4paper, margin=0.75in]{geometry}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}
\section*{}

\vspace*{8\baselineskip}
\subsection*{\uppercase{Dual Degree Project}}

\subsubsection*{Implementation of cognitive radio on the USRP kit | June 2013 - till date}

\emph{Guide: Prof S N Merchant, Dept. of Electrical Engineering, IIT Bombay}  \\*
 
\noindent $\bullet$ Carried out energy detection spectrum sensing to find the lowest energy frequency band. \\*$\bullet$ Set up calls and messages on a software defined GSM network named OpenBTS. \\*$\bullet$ Carried out a field testing of an OpenBTS network to check the interference with other nearby networks. \\*$\bullet$ Working on a cognitive OpenBTS system. 
 

\subsection*{\uppercase{Programming skills}} 

\noindent \textbf{Languages}: C, Matlab, Python, bash scripting, Assembly for the Intel 8080 microprocessor, Octave, Verilog, Ruby, SQL, XML.\\*
\textbf{Operating systems}: Unix, Linux and Mac OS X.


\subsection*{\uppercase{Course projects}} 

\subsubsection*{Scalable video coding using wavelets | Feb-Apr 2013}

\emph{Guide: Prof V M Gadre, Dept. of Electrical Engineering, IIT Bombay} \\*
  
\noindent $\bullet$ Compressed three different spatial resolutions of a video together into a single bitstream \\*
$\bullet$ At the receiving end, uncompressed the best resolution for the bit rate available. 
 
\subsubsection*{Principal Component Analysis in face recognition | Oct-Nov 2012}

\emph{Guide: Prof V Rajbabu, Dept. of Electrical Engineering, IIT Bombay} \\*
  
\noindent$\bullet$ Implemented an iterative algorithm of using PCA in face recognition. 
 

\subsubsection*{Design and test an algorithm for restoring a brain image | Sep-Nov 2012} 

\emph{Guide: Prof Arjun Arunachalam, Dept. of Electrical Engineering, IIT Bombay} \\*
  
\noindent $\bullet$ Implemented an algorithm to remove noise artifacts from a brain image. \\*
$\bullet$ Used the non-linear conjugate gradient method to optimize the estimate. 
 
\subsubsection*{A simple AM voice Transmitter | Aug-Oct 2011} 
\emph{Guide: Prof S N Merchant, Dept. of Electrical Engineering, IIT Bombay} \\*  
\noindent $\bullet$ Developed an AM voice transmitter with a carrier frequency of 1 MHz, taking input from a music player via a 3.5 mm jack.
 

\subsubsection*{Mini UID for IIT Bombay Campus | Oct-Nov 2009} 

\emph{Guide: Prof Deepak Phatak, Dept. of Computer Science and Engineering, IIT Bombay}\\*
  
\noindent $\bullet$ Automated fingerprint matching for the purposes of registration, verification and attendance.
 

\subsection*{\uppercase{Seminars}}
\subsubsection*{Measurement of interference temperature | Jan-Apr 2013} 

\emph{Guide: Prof S N Merchant, Dept. of Electrical Engineering, IIT Bombay} \\*
  
\noindent $\bullet$ Surveyed various ways of measuring interference temperature efficiently. \\*
$\bullet$ Became familiar with the concept of Cognitive Radio.
 

\subsubsection*{Led’s for high speed applications (over 100 Mbps) | Mar-Apr 2013}

\emph{Guide: Prof Joseph John, Dept. of Electrical Engineering, IIT Bombay} \\*
  
\noindent $\bullet$ Presented a seminar on how LED’s could be used for high speed fiber optic communications. \\*
$\bullet$ LED’s are cheaper, rugged and safer to handle compared to laser diodes.
 

\subsection*{\uppercase{RELEVANT COURSES}}
Digital Communications, Probability and Random Processes, Fibre Optic Communications, Communication Systems, Communications Lab, Network Theory,Advanced Computing for Electrical Engineers, Microprocessors.
\subsection*{\uppercase{Extra curricular}}

  
\noindent $\bullet$ Secured a silver medal in the All India Computer Knowledge Competition 2006. \\*
$\bullet$ `9/10' in the course EE 717: Advanced Computing for Electrical Engineers. \\*
$\bullet$ \textbf{Organizer, Infrastructure Team},Techfest 2010. \\*
$\bullet$ \textbf{Social Service}: surveyed water and electrical resources of remote villages in Maharashtra. \\*
$\bullet$ \textbf{Social Service}: taught math and physics to 6th standard students. \\*$\bullet$ \textbf{Interests}:  Computer programming for technical problems, communications, problem solving, functional programming. \\*
 

\end{document}